---
title: "Who is into Green Infrastructure"
author: "Sun Ho Hwang"
subtitle: Motivation of Green Infrastructure Participation
output: html_document
---


# Introduction

Due to global warming, one of the difficulties that the urban environment face is the increase of precipitation. There is a chance that this will lead to water pollution as the stormwater that runs through the urban impervious surface collects pollutants and enters the sewer system. There has been continuous effort to implement green infrastructure to adapt to this environmental change. However there are certain limits because this involves the voluntary participation of individual households. This study will help understand the motivation of the participants of the past rain barrel project and help guide environmental organizations to plan how to increase participation.

This project will analyze the motivation of households participating in the rain barrel project by comparing contributing factors which are the education attainment and median income at the census tract level. The education attainment and income of the people participating in this project will be represented as a map. Then the shapefile of the rain barrels will be overlapped in order to analyze the demographic characteristic of households participating in the project. 



# Materials and methods
```{r, message=F, warning=F}
#library(acs)
#install.packages("base")
library(choroplethr)
library(ggplot2)
library(choroplethrMaps)
library(ggmap)
#install.packages("mapproj")
library(mapproj)
library(maps)
library(tidycensus)
library(tidyverse)
library(kableExtra)
#knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```

## Download and clean all required data
```{r}

#register your api key
#use personal account not ub gmail account
register_google("")
#census api key
census_api_key("de66b80e57fd740d87d1af03c5c306086b4f17fa")


#Income map


#census tract level for Income, choroplethr
#?df_ny_tract_demographics
#check data
data("df_ny_tract_demographics")
View(df_ny_tract_demographics)
#make value column value
df_ny_tract_demographics$value=df_ny_tract_demographics$per_capita_income
#create a choropleth map

tract_choropleth(df_ny_tract_demographics,state_name = "new york" ,title="Per Capita Income Estimates",legend = "Dollars",num_colors = 7)

#state names

#?state.regions
data("state.regions")
View(state.regions)

#But we have to frame it


#Problem: location and time frame
#set area to Buffalo city, year should include 2015 and 2016
#area:leave and overlap with shapefile later

#Problem1.how about time frame?
#Problem2.data for Buffalo missing? How should I deal with missing values?
#maybe try again with tidycensus
#https://walker-data.com/tidycensus/articles/basic-usage.html


#2 educational attainment

#get_acs() will be used.

#search for variables
v1 <- load_variables(2019, "acs5", cache = TRUE)
View(v1)
#variable:B15003_001: total:educational attainment for population 25 years and older
#variable: B15003_001,  B15003_017 to B15003_025 will be used

#test

#educational attainment data only for total
ed<-get_acs(geography="tract",variables=c(educationtotal="B15003_001"),county="Erie",state="NY",year=2019)

view(ed)

#We need to identify the variables we are willing to use and name it again to make it understandable.
#B19019_001 will be later used for median income. This represents the total of median household income by household size. 

get_vars = c('B19019_001',paste('B15003_',sprintf('%03d',c(1,17:25)),sep=''))
names(get_vars) =  c('income','all','hs','ged','someco1','someco2',
                     'as','bac','mas','prof','doc')

edu_data = get_acs(geography = 'tract', variables = get_vars,
                   state='NY',county='Erie',geometry='TRUE')

#did I use the 5 year acs table? double check? yes

as_tibble(edu_data) %>% select(-geometry)

#classify education attainment to at least hight school and at least bachelor degree

library(tidyverse)                     
acs_spread = edu_data %>% 
    select(-moe) %>% 
    spread(key=variable,value=estimate) %>%
    mutate('atleast_hs' = (hs + ged+ someco1 + someco2 + as + bac + mas + prof + doc) / all,
           'atleast_bs' = (bac + mas + prof + doc) / all) %>%
    select(GEOID,income,atleast_hs,atleast_bs)



#Continuing..


```


Add any additional processing steps here.

# Results

[~200 words]

Tables and figures (maps and other graphics) are carefully planned to convey the results of your analysis. Intense exploration and evidence of many trials and failures. The author looked at the data in many different ways before coming to the final presentation of the data.

Show tables, plots, etc. and describe them.


# Conclusions

[~200 words]

Clear summary adequately describing the results and putting them in context. Discussion of further questions and ways to continue investigation.

# References

All sources are cited in a consistent manner



